Rectangulotopes

### 2024-04-03 draft/rectangulotopes.tex
strong submodular

% marginal comments
\usepackage{todonotes}
\newcommand{\vincent}[1]{\todo[color=blue!30]{\rm #1 \\ \hfill --- V.}}
\newcommand{\Vincent}[1]{\todo[inline, color=blue!30]{\rm #1 \\ \hfill --- V.}}
\newcommand{\jean}[2][]{\todo[size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- J.}}
\newcommand{\Jean}[2][]{\todo[inline, size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- J.}}

@@

@@

\begin{lemma}
  \label{lem:strongsum}
  The strong rectangulotope $\SRP(n)$ is realized by the Minkowski sum of all shard polytopes of yin and yang arcs.
\end{lemma}

@@

\jean{Compute the submodular functions of each yin and yang shard polytopes and sum them.}

>>>>

% marginal comments
\usepackage{todonotes}
\newcommand{\vincent}[1]{\todo[size=\scriptsize, color=blue!30]{\rm #1 \\ \hfill --- V.}}
\newcommand{\Vincent}[1]{\todo[inline, size=\scriptsize, color=blue!30]{\rm #1 \\ \hfill --- V.}}
\newcommand{\jean}[2][]{\todo[size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- J.}}
\newcommand{\Jean}[2][]{\todo[inline, size=\scriptsize, color=orange!30,#1]{\rm #2 \\ \hfill --- J.}}

@@

\jean{You may want to use another notation here, feel free.}

@@

\begin{lemma}
  \label{lem:strongMinkowski}
  The strong rectangulotope $\SRP(n)$ is realized by the Minkowski sum of all shard polytopes of yin and yang arcs.
\end{lemma}

@@

\jean{That seems to work.}

The submodular function corresponding to our realization of $\SRP(n)$ can be obtained as before by summing the functions defining the yin and yang shard polytopes in Lemmas~\ref{lem:yinsp} and~\ref{lem:yangsp}.

\begin{lemma}
  The strong rectangulotope $\SRP(n)$ is realized by the following submodular function:
  \[
  f(S) := |\{ I, J : I\cap S\not=\emptyset \wedge J\cap ([n]\setminus S) \not= \emptyset \}| +
  |\{ I, J : J\cap S\not=\emptyset \wedge I\cap ([n]\setminus S) \not= \emptyset \}|,
  \]
  where $I, J$ are pairs of consecutive and nonempty intervals of $[n]$.
\end{lemma}

\begin{proof}
  From Lemmas~\ref{lem:strongMinkowski} and~\ref{lem:submodsum}, the submodular function defining the realization of $\WRP(n)$ is the sum of the submodular functions defining the yin and yang shard polytope in Lemmas~\ref{lem:yinsp} and~\ref{lem:yangsp}. For a yin arc $A$ defined by consecutive intervals $I, J$ of $[n]$, we have that its shard polytope $\SP(A)$ is realized by the submodular function
  \[
  \yin{f}_{I,J}(S) := \llbracket S\cap I\not=\emptyset \wedge S\not\supseteq J \rrbracket .
  \]
  Similarly, for a yang arc, the shard polytope $\SP(A)$ is defined by the following submodular function:
  \[
  \yang{f}_{I,J}(S) := \llbracket S\cap J\not=\emptyset \wedge S\not\supseteq I \rrbracket .
  \]
  Their sum
  \[
  f(S) := \sum_{I,J} \yin{f}_{I,J}(S) + \yang{f}_{I,J}(S)
  \]
  is therefore as claimed.
\end{proof}
